Notes on conformal manifolds

### 2025-06-17 Draft_MLFlatDirections.tex
replace flowchart

% ---- TIKZ ----
\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning}

\tikzstyle{startstop} = [ellipse, minimum width=3.5cm, minimum height=1.cm, text centered, draw=black, fill=gray!20]
\tikzstyle{process} = [rectangle, minimum width=6cm, minimum height=1.2cm, text centered, draw=black, fill=myblue!75]
\tikzstyle{decision} = [rectangle, minimum width=5cm, minimum height=1.2cm, text centered, draw=black, fill=myorange!100, aspect=2]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

  In algebraic geometry, the set of solutions to the equations $\nabla V = 0$ defines an algebraic variety over a certain base field. In our case, the potential $V$ and its gradient $\nabla V$ are polynomial functions with
  \begin{center}
  	\begin{minipage}{18cm}
  		\begin{tcolorbox}[colback=myblue!5,
  			colframe=myblue,
  			title=Algorithm flowchart for ASMC algorithm,
  			halign title=flush center,
  			sharp corners
  			]
  			%	\scalebox{0.5}{
  				\begin{tikzpicture}[node distance=1.8cm and .5cm]

  					% Nodes
  					\node (start) [startstop] {Start};

  					\node (init_particles) [process, below of=start] {Initialize sparse polynomials};
  					\node (set_weights) [process, below of=init_particles] {Initialize weights and variables};
  					\node (compute_beta) [process, below of=set_weights] {Compute or adapt temperature $\beta$};
  					\node (weight_update) [process, below of=compute_beta] {Compute log-targets and update weights};

  					\node (ess_check) [decision, below of=weight_update] {Is ESS $<$ Threshold?};
  					\node (resample) [process, right=4.25cm of ess_check] {Resample particles};

  					\node (mutation) [process, below of=ess_check, yshift=-0.5cm] {Apply MH mutation to particles};
  					\node (acceptance) [process, below of=mutation] {Compute acceptance and update best};

  					\node (end_iter) [decision, below of=acceptance] {Is this the last iteration?};

  					\node (exploit) [process, below of=end_iter, yshift=-0.5cm] {Optional local search (exploitation)};
  					\node (output) [process, below of=exploit] {Return best coefficients and logs};
  					\node (stop) [startstop, below of=output] {Stop};

  					% Arrows
  					\draw [arrow] (start) -- (init_particles);
  					\draw [arrow] (init_particles) -- (set_weights);
  					\draw [arrow] (set_weights) -- (compute_beta);
  					\draw [arrow] (compute_beta) -- (weight_update);
  					\draw [arrow] (weight_update) -- (ess_check);

  					\draw [arrow] (ess_check) -- node[above] {Yes} (resample);
  					\draw [arrow] (resample) |- (mutation);

  					\draw [arrow] (ess_check) -- node[left] {No} (mutation);
  					\draw [arrow] (mutation) -- (acceptance);
  					\draw [arrow] (acceptance) -- (end_iter);

  					\draw [arrow] (end_iter) -- node[left] {} ++(-4,0) |- (compute_beta);
  					\node [pos=10, below=430pt, xshift=-100pt] {No};
  					\draw [arrow] (end_iter) -- node[right] {Yes} (exploit);

  					\draw [arrow] (exploit) -- (output);
  					\draw [arrow] (output) -- (stop);
  				\end{tikzpicture}
  			\end{tcolorbox}
  		\end{minipage}
  	\end{center}
  	coefficients lying in a specific field extension of $\mathbb{Q}$—typically of the form $\mathbb{Q}(\sqrt{d_1}, \sqrt{d_2}, \dots)$, where $d_i \in \mathbb{Q}$. That is, the coefficients of the polynomials are combinations of rational numbers and square roots of rational numbers.

>>>>

% ---- TIKZ ----
\usepackage{tikz}
\usepackage{tcolorbox}
\usetikzlibrary{calc}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning}

% Définition des couleurs modernes
\definecolor{deepblue}{RGB}{41, 128, 185}
\definecolor{lightblue}{RGB}{174, 214, 241}
\definecolor{emerald}{RGB}{46, 204, 113}
\definecolor{lightemerald}{RGB}{212, 245, 227}
\definecolor{coral}{RGB}{231, 76, 60}
\definecolor{lightcoral}{RGB}{250, 215, 212}
\definecolor{charcoal}{RGB}{52, 73, 94}
\definecolor{lightgray}{RGB}{150, 150, 150}

% Styles épurés et modernes
\tikzstyle{startstop} = [
ellipse, 
minimum width=3cm, 
minimum height=1cm, 
text centered, 
draw=charcoal, 
fill=lightgray,
line width=1.2pt,
font=\sffamily\small\bfseries
]

\tikzstyle{process} = [
rectangle, 
minimum width=5.5cm, 
minimum height=1.1cm, 
text centered,
draw=myblue, 
fill=lightblue,
line width=1pt,
rounded corners=2pt,
font=\sffamily\small
]

\tikzstyle{decision} = [
rectangle, 
minimum width=3.2cm, 
minimum height=1.cm, 
text centered, 
draw=coral, 
fill=lightcoral,
line width=1pt,
font=\sffamily\small\bfseries,
aspect=1.3
]

\tikzstyle{arrow} = [
thick,
->,
>=Stealth,
color=charcoal,
line width=1.5pt
]

\tikzstyle{arrow_label} = [
font=\sffamily\small\bfseries,
color=charcoal
]

@@

  In algebraic geometry, the set of solutions to the equations $\nabla V = 0$ defines an algebraic variety over a certain base field. In our case, the potential $V$ and its gradient $\nabla V$ are polynomial functions with
\begin{center}
	\begin{minipage}{16cm}
		\begin{tcolorbox}[
			colback=white,
			colframe=myblue,
			title=\textbf{Algorithme ASMC - Diagramme de flux},
			fonttitle=\sffamily\large,
			halign title=flush center,
			boxrule=2pt,
			left=6pt,
			right=6pt,
			top=8pt,
			bottom=8pt
			]
			\begin{tikzpicture}[node distance=1.6cm and 0.8cm, scale=0.85, transform shape]

				% Nœuds
				\node (start) [startstop] {Start};

				\node (init_particles) [process, below of=start] {Initialize particles et weights};

				\node (compute_beta) [process, below of=init_particles] {Compute/adapt inverse temperature $\beta$};

				\node (weight_update) [process, below of=compute_beta] {Compute losses and update weights};

				\node (ess_check) [decision, below of=weight_update] {ESS $<$ Threshold ?};

				\node (resample) [process, right=3.8cm of ess_check] {Resampling particles};

				\node (mutation) [process, below of=ess_check, yshift=-0.4cm] {Mutate particles with Metropolis Hasting proposal};

				\node (acceptance) [process, below of=mutation] {Accept/Reject particles};

				\node (end_iter) [decision, below of=acceptance] {Last step ?};

				\node (exploit) [process, below of=end_iter, yshift=-0.4cm] {Optional local search};

				\node (output) [process, below of=exploit] {Return current particles};

				\node (stop) [startstop, below of=output] {End};

				% Flèches avec étiquettes améliorées
				\draw [arrow] (start) -- (init_particles);
				\draw [arrow] (init_particles) -- (compute_beta);
				\draw [arrow] (compute_beta) -- (weight_update);
				\draw [arrow] (weight_update) -- (ess_check);

				\draw [arrow] (ess_check) -- node[above, arrow_label] {Yes} (resample);
				\draw [arrow] (resample) |- (mutation);

				\draw [arrow] (ess_check) -- node[left, arrow_label] {No} (mutation);
				\draw [arrow] (mutation) -- (acceptance);
				\draw [arrow] (acceptance) -- (end_iter);

				% Boucle de retour améliorée
				\draw [arrow] (end_iter) -| node[pos=0.25, below, arrow_label] {Non} ++(-4.5,0) |- (compute_beta);

				\draw [arrow] (end_iter) -- node[right, arrow_label] {No} (exploit);
				\draw [arrow] (exploit) -- (output);
				\draw [arrow] (output) -- (stop);

			\end{tikzpicture}
		\end{tcolorbox}
	\end{minipage}
\end{center}
%  \begin{center}
%  	\begin{minipage}{18cm}
%  		\begin{tcolorbox}[colback=myblue!5,
%  			colframe=myblue,
%  			title=Algorithm flowchart for ASMC algorithm,
%  			halign title=flush center,
%  			sharp corners
%  			]
%  			%	\scalebox{0.5}{
%  				\begin{tikzpicture}[node distance=1.8cm and .5cm]
%  					
%  					% Nodes
%  					\node (start) [startstop] {Start};
%  					
%  					\node (init_particles) [process, below of=start] {Initialize sparse polynomials};
%  					\node (set_weights) [process, below of=init_particles] {Initialize weights and variables};
%  					\node (compute_beta) [process, below of=set_weights] {Compute or adapt temperature $\beta$};
%  					\node (weight_update) [process, below of=compute_beta] {Compute log-targets and update weights};
%  					
%  					\node (ess_check) [decision, below of=weight_update] {Is ESS $<$ Threshold?};
%  					\node (resample) [process, right=4.25cm of ess_check] {Resample particles};
%  					
%  					\node (mutation) [process, below of=ess_check, yshift=-0.5cm] {Apply MH mutation to particles};
%  					\node (acceptance) [process, below of=mutation] {Compute acceptance and update best};
%  					
%  					\node (end_iter) [decision, below of=acceptance] {Is this the last iteration?};
%  					
%  					\node (exploit) [process, below of=end_iter, yshift=-0.5cm] {Optional local search (exploitation)};
%  					\node (output) [process, below of=exploit] {Return best coefficients and logs};
%  					\node (stop) [startstop, below of=output] {Stop};
%  					
%  					% Arrows
%  					\draw [arrow] (start) -- (init_particles);
%  					\draw [arrow] (init_particles) -- (set_weights);
%  					\draw [arrow] (set_weights) -- (compute_beta);
%  					\draw [arrow] (compute_beta) -- (weight_update);
%  					\draw [arrow] (weight_update) -- (ess_check);
%  					
%  					\draw [arrow] (ess_check) -- node[above] {Yes} (resample);
%  					\draw [arrow] (resample) |- (mutation);
%  					
%  					\draw [arrow] (ess_check) -- node[left] {No} (mutation);
%  					\draw [arrow] (mutation) -- (acceptance);
%  					\draw [arrow] (acceptance) -- (end_iter);
%  					
%  					\draw [arrow] (end_iter) -- node[left] {} ++(-4,0) |- (compute_beta);
%  					\node [pos=10, below=430pt, xshift=-100pt] {No};
%  					\draw [arrow] (end_iter) -- node[right] {Yes} (exploit);
%  					
%  					\draw [arrow] (exploit) -- (output);
%  					\draw [arrow] (output) -- (stop);
%  				\end{tikzpicture}
%  			\end{tcolorbox}
%  		\end{minipage}
%  	\end{center}
  	coefficients lying in a specific field extension of $\mathbb{Q}$—typically of the form $\mathbb{Q}(\sqrt{d_1}, \sqrt{d_2}, \dots)$, where $d_i \in \mathbb{Q}$. That is, the coefficients of the polynomials are combinations of rational numbers and square roots of rational numbers.
